### 2025-08-23 multiple-regression.qmd
20250823 - flesh out transformation

```{r}
obj <- bestNormalize::bestNormalize(player_stats_seasonal$fantasyPoints)
player_stats_seasonal$fantasyPoints_transformed <- predict(obj)

# Can back-transform transformed values back to the original metric later if needed:
original <- predict(
  obj,
  newdata = player_stats_seasonal$fantasyPoints_transformed,
  inverse = TRUE)
```

>>>>

```{r}
bnTransformed <- bestNormalize::bestNormalize(player_stats_seasonal$fantasyPoints)
```

Here are the transformation results—in this case, the best-fitting transformation is an ordered quantile (ORQ) normalization transformation:

```{r}
bnTransformed
```

Then, we apply the best-fitting transformation to the variable, to create a transformed variable that is more normally distributed.

```{r}
player_stats_seasonal$fantasyPoints_transformed <- predict(bnTransformed)

# Can back-transform transformed values back to the original metric later if needed:
original <- predict(
  bnTransformed,
  newdata = player_stats_seasonal$fantasyPoints_transformed,
  inverse = TRUE)
```
